Current Sheets in the Solar Wind: Parker Solar Probe Observations

### 2024-08-28 presentations/rMeeting.qmd
chore: update website

---
title: "Current Sheets in the Solar Wind: Parker Solar Probe Observations"
subtitle: SPARTHB
author:
  - name: Zijin Zhang
  - name: Anton V. Artemyev
  - name: Vassilis Angelopoulos
format:
  html: default
  pptx:
    slide-level: 2
slide-number: true
date: "2024-05"
---

>>>>

---
title: "Current Sheets in the Solar Wind: Parker Solar Probe Observations"
author:
  - name: Zijin Zhang
  - name: Anton V. Artemyev
  - name: Vassilis Angelopoulos
date: "2024-05"
---
